---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Gibbon-transfer-learning-multispecies

<!-- badges: start -->
<!-- badges: end -->

This is the GitHub repository for the paper:

Clink DJ, Kim J, Cross-Jaya H, Ahmad AH, Hong M, Sala R, Birot H, Agger C, Vu TT, Thi HNT, Chi TN, and H. Klinck. (under review). Automated detection of gibbon calls from passive acoustic monitoring data using convolutional neural networks in the ‘torch for R’ ecosystem.

This repo relies on the 'gibbonNetR' package that can be installed from GitHub using the following code.
```{r, eval=FALSE }
# If you don't have devtools installed
install.packages("devtools")

# Install gibbonNetR
devtools::install_github("https://github.com/DenaJGibbon/gibbonNetR")

```

For a tutorial see: https://github.com/DenaJGibbon/gibbonNetR.


## Description of 'data' folders

1. **Folder Name:** `calldensityplots`
   - **Description:** Contains GPS data and image selections for call density plots.

2. **Folder Name:** `GPSData`
   - **Description:** Contains GPS data files.
   - **Content:** Provides location data for all recording units. Includes a script to process and create a .csv file with the points.

3. **Folder Name:** `imagesforpub`
   - **Description:** Holds spectrogram images intended for publication.

4. **Folder Name:** `ImagesforpubSoundFiles`
   - **Description:** Stores sound files corresponding to images intended for publication.

5. **Folder Name:** `testimages`
   - **Description:** Stores test images for model evaluation. Test data sourced from Maliau Basin or Dakrong Nature Preserve.

6. **Folder Name:** `training_images_sorted`
   - **Description:** Contains sorted training images. Images sorted to ensure training, validation, and test sets contain clips from different recordings.

---

## Description of R scripts

1. **Script Name:** `Part 1. Train CNNs on gibbon data.R`
   - **Description:** Trains Convolutional Neural Networks (CNNs) on gibbon data.

2. **Script Name:** `Part 2. Evaluate performance on test datasets.R`
   - **Description:** Evaluates model performance on test datasets.

3. **Script Name:** `Part 3. Evaluate performance with annotated filesV2.R`
   - **Description:** Evaluates model performance with annotated files (version 2).

4. **Script Name:** `Part 4. Selection Table Model Performance Evaluation .R`
   - **Description:** Evaluates model performance on a wide array of data using selection tables output by 'gibbonNetR'.

5. **Script Name:** `Part 5. Deploy Model over PAM data.R`
   - **Description:** Deploys model over passive acoustic monitoring (PAM) data. NOTE: Due to the size constraints we cannot make these data publicly available.

6. **Script Name:** `Part 6. Call Density Plots.R`
   - **Description:** Generates call density plots.

7. **Script Name:** `Part 7. Spectrograms for publication .R`
   - **Description:** Generates spectrograms for publication.
